Software Clusterings with Vector Semantics and the Call Graph

### 2019-04-28 manuscript/manuscript.tex
Fix commas

For the prepossessing stage use the NLP package spaCy \cite{spacy} which provided us with very useful tools for the extraction. 
After prepossessing, we use Gensim \cite{gensim} to train the Doc2Vec model. 
First of all, we tokenize the code and remove the stop-words. 
After that, for each token, we split it into its constituent parts using dynamic programming \cite{wordninja} and lemmatize 
each individual sub-token. 
For example the method \texttt{\_\_zone\_seqlock\_init} corresponds to \texttt{zone}, \texttt{seqlock} and \texttt{init}, 
\texttt{inprogress} is split into \texttt{in} and \texttt{progress} and \texttt{literals} becomes \texttt{literal}.

@@

\paragraph{Implementation}  
Our method is implemented in the Python Language using spaCy\cite{spacy} Gensim \cite{gensim} and NetworkX \cite{nx}.

\paragraph{Decision Rationale for Evaluation System} 
We have chosen to use Linux as a codebase to evaluate our method on 
since it is a large and complex system with 27 years of continuous development, spanning 20.3 millions source lines of code (SLOC) at the time of writing.  
Moreover, it is easy to find ground truth system due to its clear directory structure and construct test-cases for
evaluations. 
Finally, it was also used in related studies \cite{acdc, evaluation} as a reference system for evaluation.

\paragraph{Experimental Setting} Our method was run on Linux 4.21,
consisting of 20.3 million SLOC against Average-Linkage \cite{average}, Complete-Linkage \cite{complete} 
and Ward-Linkage \cite{ward} using the same document embeddings
as well as ACDC with structural information \cite{acdc} and LIMBO \cite{limbo} with $B = 100$, $S = \infty$ and Bag-of-Words features. The results are presented in Table \ref{tab:evaluation}. 
As ground truth we have used the first level directories as a target clustering and as input we have considered 
the modules of the one-top directories. 
For example, the source code file \texttt{drivers/net/ieee802154\-/mcr20a.c} has a ground truth value of \texttt{drivers} 
and it is considered under the same module as every \texttt{.c} and \texttt{.h} file under \texttt{drivers/net/ieee802154}. 
As a clustering distance measure we have used the MoJo distance measure, as proposed in reference \cite{mojo}. 
Since, Louvain Community Detection produces  different (but very similar) results every time it runs, we ran the simulations 
multiple times and averaged the results.

@@

\section{Conclusions} This paper is set out to show how we can use a combination of vector semantics
and information from the call graph in order to produce meaningful clusterings of a software system.
We conclude that we have outperformed state-of-the-art software clusterings and conventional
agglomerative clustering algorithms 
in terms of \emph{extremity}, \emph{authoritativeness} and \emph{stability} 
without knowing the number of clusters of the Ground Truth. This evidence strongly
supports the further usage of vector semantics and the call graph for architecture recovery.
Finally, further work is encouraged in several areas such as 
integration with more static analyzers and use of the project in order to recover layered architectures.

>>>>

For the prepossessing stage use the NLP package spaCy \cite{spacy} which provided us with very useful tools for the extraction. 
After prepossessing, we use Gensim \cite{gensim} to train the Doc2Vec model. 
First of all, we tokenize the code and remove the stop-words. 
After that, for each token, we split it into its constituent parts using dynamic programming \cite{wordninja} and lemmatize 
each individual sub-token. 
For example, the method \texttt{\_\_zone\_seqlock\_init} corresponds to \texttt{zone}, \texttt{seqlock} and \texttt{init}, 
\texttt{inprogress} is split into \texttt{in} and \texttt{progress} and \texttt{literals} becomes \texttt{literal}.

@@

\paragraph{Implementation}  
Our method is implemented in the Python Language using spaCy\cite{spacy}, Gensim \cite{gensim} and NetworkX \cite{nx}.

\paragraph{Decision Rationale for Evaluation System} 
We have chosen to use Linux as a codebase to evaluate our method on 
since it is a large and complex system with 27 years of continuous development and spanning 20.3 millions source lines of code (SLOC) at the time of writing.  
Moreover, it is easy to find ground truth system due to its clear directory structure and construct test-cases for
evaluations. 
Finally, it was also used in related studies \cite{acdc, evaluation} as a reference system for evaluation.

\paragraph{Experimental Setting} Our method was run on Linux 4.21,
consisting of 20.3 million SLOC against Average-Linkage \cite{average}, Complete-Linkage \cite{complete} 
and Ward-Linkage \cite{ward} using the same document embeddings
as well as ACDC with structural information \cite{acdc} and LIMBO \cite{limbo} with $B = 100$, $S = \infty$ and Bag-of-Words features. The results are presented in Table \ref{tab:evaluation}. 
As ground truth we have used the first level directories as a target clustering and as input we have considered 
the modules of the one-top directories. 
For example, the source code file \texttt{drivers/net/ieee802154\-/mcr20a.c} has a ground truth value of \texttt{drivers} 
and it is considered under the same module as every \texttt{.c} and \texttt{.h} file under \texttt{drivers/net/ieee802154}. 
As a clustering distance measure we have used the MoJo distance measure, as proposed in reference \cite{mojo}. 
Since Louvain Community Detection produces  different (but very similar) results every time it runs, we ran the simulations 
multiple times and averaged the results.

@@

\section{Conclusions}

This paper is set out to show how we can use a combination of vector semantics
and information from the call graph in order to produce meaningful clusterings of a software system.
We conclude that we have outperformed state-of-the-art software clusterings and conventional
agglomerative clustering algorithms 
in terms of \emph{extremity}, \emph{authoritativeness} and \emph{stability} 
without even knowing the number of clusters of the Ground Truth. This evidence strongly
supports the further usage of vector semantics and the call graph for architecture recovery.
Finally, further work is encouraged in several areas such as 
integration with more static analyzers and use of the project in order to recover layered architectures.
